%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Metin}{Akın}{ \urlstyle{same}\url{http://metoinside.com} \\
\href{mailto:hey@metoinside.com}{hey@metoinside.com} | +90 (507) 056 2028
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{Yıldız Tech. University}
\descript{MEng in Electronics Engineering}
\location{Expected Jan 2018 | Istanbul, TR \\ Cum. GPA: N/A}
\sectionsep

\subsection{Riga Tech. University}
\descript{Erasmus Exchange Semester }
\location{Jan-Jun 2012 | Riga, LV}
\sectionsep


\subsection{Bilecik S.E. University}
\descript{BS in Electrical-Electronics Engineering}
\location{Grad. August 2013 | Bilecik, TR}
\location{ Cum. GPA: 2.96 / 4.0 }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/metoinside}{\custombold{\textcolor{blue}{metoinside}}} \\
LinkedIn://  \href{https://www.linkedin.com/in/metoinside}{\custombold{\textcolor{blue}{metoinside}}} \\
Twitter://  \href{https://twitter.com/metoinside}{\custombold{\textcolor{blue}{metoinside}}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Machine Learning \\
Software Engineering \\
\sectionsep

\subsection{Undergraduate}
\href{https://s3.amazonaws.com/verify.edx.org/downloads/da8f6310cc1d4955b810a45a3f79d526/Certificate.pdf}{\textcolor{blue}{Embedded Systems}} \\
\href{https://s3.amazonaws.com/verify.edx.org/downloads/6ec0a7e04dd64df5aa47a653321fbf57/Certificate.pdf}{\textcolor{blue}{Introduction to Linux}} \\
Fuzzy Logic \\
Computer Vision \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Python \textbullet{}   C++ \textbullet{} C \textbullet{} MATLAB \\
HTML \textbullet{} CSS \textbullet{} PHP \\
\location{Familiar:}
Java \textbullet{} Android \textbullet{} MySQL \textbullet{} Git
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Hobbies
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hobbies}
Cycling \textbullet{}  Running \textbullet{} Reading \\
Spray-Painting \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\href{http://www.upwork.com/}{\runsubsection{\underline{Upwork}}}
\descript{| Freelancer }
\location{Mar 2015 – March 2016 | Istanbul, Turkey}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Virtual Assistance for an international procurement company -- \custombold{\href{http://www.markit.eu/}{\textcolor{blue}{MartIT}}}
\item Kocaeli Science Center installation for TUBITAK -- \custombold{\href{http://www.roto.com/}{\textcolor{blue}{Roto}}} 
\item Website development -- \custombold{\href{http://tekirdagosgb.com/}{\textcolor{blue}{Tekirdag Occupational Health\&Safety}}}
\item Market research and distributor analysis -- \custombold{\href{http://www.dokito.it/en/}{\textcolor{blue}{Dicos Group}}}
\item Sample collection of Turkish Speakers for Speech Recognition - \custombold{\href{http://www.1a-voices.com}{\textcolor{blue}{1-a Voices}}} 
\end{tightemize}
\sectionsep

\href{http://letsdoitturkiye.org.tr/}{\runsubsection{\underline{Let's Do It! Türkiye}}}
\descript{| Country Coordinator }
\location{Nov 2014 – Feb 2016 | Istanbul, Turkey}
\begin{tightemize}
\item Organised \custombold{\href{http://cleanworldconference2016.com/}{\textcolor{blue}{Clean World Conference 2016}}} in Bursa with 110 international participants from 40 countries. Please click to watch the \custombold{\href{https://www.youtube.com/watch?v=ceG35xhbVVY}{\textcolor{blue}{video}}}
\item Lead a single day, nationwide clean up action accross the country
\item Provide instructions and promotional materials for teams in various cities
\item Lead a clean-up action in Belgrad Forests of Istanbul with 200 people attendance from corporate firms, NGOs, university clubs
\end{tightemize}
\sectionsep

\href{http://www.bsh-group.com.tr/}{\runsubsection{\underline{B/S/H/ Turkey}}}
\descript{| Master Student Program, Quality Department }
\location{Aug 2014 – Dec 2015 | Tekirdag, Turkey}
\begin{tightemize}
\item Keep track of the Key Performance Indicators from Customer Experience
\item Find an efficient way of testing procedures of the returning parts and appliances 
\item Created purchase orders for creating a new testing lab
\end{tightemize}
\sectionsep

\href{http://infron.com.tr/}{\runsubsection{\underline{Infron Ltd}}}
\descript{| Software Engineer }
\location{Mar 2014 – Feb 2015 | Istanbul, Turkey}
\begin{tightemize}
\item Worked on the hardware and software development of palm-size ECG device.
\item Mainly Qt framework used for development.
\item Implemented DICOM standard with open-source libraries into the device.
\item After sales support, maintain marketing and PR operations.
\end{tightemize}
\sectionsep

\href{http://www.accenture.com/lv-en/}{\runsubsection{\underline{Accenture Latvia}}}
\descript{| Testing Team Member \& Intern}
\location{Jun 2012 – Sep 2012 | Riga, Latvia \& Pune, India}
\begin{tightemize}
\item Implemented ~1000 test cases with the team of 6 people \\
\item Product was built for customs of EU member states with C++ and tested manually \\
\item Worked smoothly with the specification and development team \\

\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Blogging
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Blogging}
\href{http://metoinside.com/}{\runsubsection{metoinside.com}}

\location{Jan 2010 – Present | Turkey}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Publication
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publication}
\begin{tabular}{rll}
Turkish         & \href{http://www.isites.info/PastConferences/ISITES2013/}{ISITES 2013}  & \href{http://www.isites.info/PastConferences/ISITES2013/}{\textcolor{blue}{Safety Audit With Imaging Systems For Level Crossing Areas}}  \\

\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies}

\begin{tabular}{rll}
2016 -      & Board Member    & \href{http://siyamder.org/}{\textcolor{red}{Civil Life Association}} \\
2015 -      & Founder    & \href{http://kocaeliturkcetoastmasters.org/}{\textcolor{red}{Kocaeli Turkish Toastmasters}} \\
2014 -      & Board Member    & \href{http://toplumsalarge.org/}{\textcolor{blue}{Association of R\&D on Societal Issues}} \\
2013 - 2015     & Member    & \href{http://istanbultoastmasters.org/}{\textcolor{blue}{Istanbul Toastmasters}} \\
2013 - 2014    & Member    & IEEE \\
\end{tabular}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}